Comparative analysis of PMV Models accuracy implemented in the ISO 7730:2005 and ASHRAE 55:2023

### 2024-10-04 Manuscript/src/sections/titleAbstract.tex
feat(abstract): highlights and graphical abstract

>>>>

    \begin{graphicalabstract}
        \includegraphics[width=\linewidth]{figures/graphical_abstract}
    \end{graphicalabstract}

    % Research highlights
    \begin{highlights}
        \item We compared the accuracy the \ac{pmv} model in the \gls{7730} and \gls{55}.
        \item Both models have low and similar prediction accuracy (\qty{34}{\percent}).
        \item The \ac{pmv-ce} has higher bias than \ac{pmv} in predicting thermal sensation.
        \item We recommend limiting the applicability range of the models to $\mid$\ac{pmv}$\mid \leq 0.5$.
        \item Individuals who feel slightly warm/cool are not thermally neutral.
    \end{highlights}
